%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1cm,right=6.9cm,marginparwidth=5cm,marginparsep=0.9cm,top=1.25cm,bottom=1.25cm}

\lefthyphenmin=100
\tolerance=1000

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

\usepackage{hyperref}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{DarkGrey}{HTML}{333333}
\colorlet{heading}{FireBrick}
\colorlet{accent}{FireBrick}
\colorlet{emphasis}{black}
\colorlet{body}{DarkGrey}
\colorlet{link}{FireBrick}

\hypersetup{
    colorlinks=true,
    linkcolor=link,
    filecolor=link,      
    urlcolor=link,
}
\urlstyle{same}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Edward Pierzchalski}
\tagline{Software Engineering Pragmatist and Formal Methods Enthusiast}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{e.a.pierzchalski@gmail.com}
  \phone{+61 404 664 375}
  \location{Sydney, Australia}

  \linkedin{linkedin.com/in/edward-pierzchalski}
  \github{github.com/pierzchalski}

%    web: www.techchain.me
%   \github{github.com/mmayer} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Proof Engineer}{CSIRO's Data61}{July 2018 -- Ongoing}{}
\begin{itemize}
\item Worked in small teams on long-running projects (2-8 people, 6+ months) on a large codebase: \href{https://github.com/seL4/l4v}{L4V} contains over one million lines of proof code, including proof automation written in SML.
\item Developed tools to detect and remove redundant proof code, saving one month of FTE development time so far.
\item Smoothed the onboarding experience by improving the initial user machine environment, writing up documentation and tutorials on Isabelle internals, and updating our internal setup instructions.
\item Produced various quality-of-life enhancements for fellow proof engineers, by specialising in the arcane internals of the Isabelle theorem prover.
\item Ported the SIMPL-GraphLang automatic semantics refinement tool from ARM to RISCV. This is a critical component in the verification of binary functional correctness.
\end{itemize}

\divider

\cvevent{Software Engineer}{Cog Systems}{January 2017 -- June 2018}{}
\begin{itemize}
\item Worked in small, rapidly changing teams (3-7 people, 1-4 month stretches) in large codebases: \texttt{wpa\_supplicant}, Android's initialisation processes, the OKL4 hypervisor.
\item Ported the OKL4 hypervisor to the imx8MQ platform, up to the point of booting a native Linux guest. Rapidly learnt how to use JTAG and Lauterbach in the process.
\item Wrangled our remote, IP-siloed git repositories using local remotes, after noticing project inefficiencies from diverging histories.
\item Designed and implemented OKL4 and linux drivers and tooling, to test all of physical memory for sentinel values in a hypervised system.
\item Pushed for and investigated migrating Cog's custom build system over to CMake.
\item Wrote a tool to extract data from device tree files into an internal specification format.
\item Modified WPA Supplicant to reject legal but insecure CA certificates, as part of a project to produce a FIPS-140 certified phone.
\item Designed an isolated keystore component for disk encryption, and modified the Android init process to use it.
\end{itemize}

\divider

\cvevent{Research Assistant}{CSIRO's Data61}{July 2014 -- November 2015; February 2016 -- November 2016}{}
\begin{itemize}
\item Independently investigated formal semantics for concurrent, security-sensitive programs, focusing on data-value-dependent classification, then proving properties using Isabelle.
\end{itemize}

\vspace{3mm}

\cvevent{Software Engineering Intern}{Google Australia}{November 2015 -- February 2016}{}
\begin{itemize}
\item Worked on extracting and indexing popular content from Google+ text posts, largely independently within a small team of 6 people.
%\item Communicated and coordinated with offsite teams, and demonstrated an ability to familiarize myself with internal tools.
\end{itemize}

\vspace{3mm}

\cvevent{Software Engineering Intern}{FoodBank Local}{November 2013 -- February 2014}{}
\begin{itemize}
\item Integrated novel logistics optimisation software as part of a startup incubation collaboration with NICTA, while rapidly upskilling in Scala. Worked tightly with a small team of 6 people.

\end{itemize}

\clearpage

\end{document}
