%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%       PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{cv_templates/cv_13/structure.tex} % Include the file specifying document layout

\usepackage{setspace}

\singlespacing

%----------------------------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
%       NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Edward Pierzchalski} % Print the main header

\begin{tabbing}
 \hspace{0.2\textwidth} \= \hspace{0.3\textwidth} \= \hspace{0.2\textwidth} \= \kill
 {\bf Address} \> 521 Anzac Parade \> {\bf Phone} \> +61 404 664 375 \\
 \> Kingsford NSW 2032 \> {\bf Email} \> \href{mailto:e.a.pierzchalski@gmail.com}{e.a.pierzchalski@gmail.com} \\
 {\bf Date of Birth} \> $15^{th}$ July 1993 \\
\end{tabbing}


%-------------------------------------------
%       EDUCATION SECTION
%-------------------------------------------

\section{Education}

\tabbedblock{
\bf{2011 -} \> BSc Mathematics, BSc Computer Science - 
\href{https://www.unsw.edu.au/}{University of New South Wales} \\
\bf{Current}\>Distinction average mark. Expected graduation in June 2016.\\[5pt]
\>\begin{minipage}{\smallertextwidth}
\setlength{\parskip}{5pt}
\vspace{5pt}
\subsection{Awards}

\textit{Google Third Year Prize}, 2013

\textit{Computer Science and Engineering Third Year Undergraduate Performance Prize (4th in year)}, 2013

\vspace{-5pt}
\subsection{Notable Projects}
\vspace{-5pt}
\begin{description}

\item[\textbf{Concepts in Programming Languages:}] Implemented a simplified Haskell-esque language, including extensions such as type inference, recursive bindings, and handling user-provided type signatures. Learnt many important concepts for understanding and modelling the semantics of programs and programming languages. Ranked $1^{st}$ in the course.

\item[\textbf{Advanced Verification:}] Verified a small C program using Isabelle, a theorem prover. Gained insight into modern software verification tools and techniques, especially proof automation. Ranked $1^{st}$ in the course.

\item[\textbf{Systems Capacity Planning:}] Constructed a Monte Carlo simulation to investigate the effects of resource network structure on performance. Achieved a high distinction in the course.

\end{description}

\end{minipage}
}

%-------------------------------------------
%       EMPLOYMENT HISTORY SECTION
%-------------------------------------------

\section{Employment}

\job
{Mar 2014 -}{Present}
{National ICT Australia}
{http://www.nicta.com.au/}
{Software Intern}
{Engineer on the \textit{Perentie} team, an experimental software verification tool written in Scala. Participated in SV COMP 2015, a software verification competition. \textit{Perentie} ranked third in its category after less than a year of development.

\begin{itemize}
 \item{Designed intermediate languages to represent and simplify C program semantics}
 \item{Helped design and implement an embedded domain-specific language for interacting with SMT solvers}
 \item{Worked on novel verification algorithms for inter-procedural analysis with an active researcher in the field}
\end{itemize}
}

\newpage

\job
{Dec 2013 -}{Sep 2014}
{Tomorrowland Enterprises}
{}
{Software Engineer}
{Worked with FoodBank Australia to produce a real-time vehicle logistics optimisation tool, written in Scala.

\begin{itemize} 
 \item{Implemented a failure-resistant `micro-service' to responsively handle events while maintaining efficient vehicle routing.}
 \item{Helped architect the project with a focus on safety by using language features to statically check business logic assumptions} 
\end{itemize}
}

%-------------------------------------------
%       IT/COMPUTING SKILLS SECTION
%-------------------------------------------

\section{Software Engineering Skills}

\begin{itemize}
\item{Experienced in developing software in small to medium teams}

\item{Strong background on functional programming, language design and semantics, and type theory}

\item{\textbf{Experienced} in Scala, Haskell, and Java}

\item{\textbf{Proficient} in Python, Bash, C, Erlang, Rust, and \LaTeX}

\end{itemize}

%-------------------------------------------

\end{document}